Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-03-24 article/02_Materials_and_Methods.Rmd
code refactoring

2. Removing all dates without age information or age information outside of the limits of the Intcal13 calibration curve: 71 - 46401 BP [@reimer_intcal13_2013]. (`r r("size bronze", sf_prep)` dates)

@@

4. Reducing date selection to all dates whose $2\sigma$ calibrated age range overlap by at least one year with the predefined window of interest: 2200 -- 800 calBC. (`r r("size bronze0", sf_prep)` dates)

5. Reducing the date selection to all dates taken from graves as indicated by the *feature type* variable. (`r r("size bronze05", sf_prep)` dates)

@@

8. Reducing date selection to dates within the research area. (`r r("size bronze15", sf_prep)` dates)

9. Removing ^14^C date doubles with tools of c14bazAAR. (`r r("size bronze16", sf_prep)` dates)

10. Transforming data from the meaning *^14^C dates on graves* to *burial type at a certain time*. For `r r("bronze15 multi dates one grave", sf_prep)` entries in the thus far assembled subset the attribution to *site* and *feature* is not unique. That means that for many graves multiple (up to 8) ^14^C dates have been created (and entered in Radon-B) and dates therefore cannot be treated as semantically equal to graves. There is a variety of phenomena that cause this effect: In some cases, safety measurements were taken so that there are multiple dates for one single grave that all fall within the margin of errors of each other. In other cases, the set of dates for one grave strongly diverge because they cover the life cycle of a collective grave that was used for hundreds of years. There are also cases where the *feature* information in Radon-B is not sufficient to determine whether two dates are really from the same grave despite the identical entry. The following steps were applied to solve this problem algorithmically. The approach is compatible with the intention to create a cultural trait time series as explained below. (`r r("size bronze17", sf_prep)` graves)

@@

    2. For the remaining `r r("bronze16 multi dates one grave with numbers", sf_prep)` problematic cases, groups were created by *site* and *feature*. The cumulated timespan covered by the $2\sigma$ age range of all these dates were taken as the relevant timespan for the respective grave.

>>>>

2. Removing all dates without age information or age information outside of the limits of the Intcal13 calibration curve: 71 - 46401 BP [@reimer_intcal13_2013]. (`r r("size dates_calibrated", sf_prep)` dates)

@@

4. Reducing date selection to all dates whose $2\sigma$ calibrated age range overlap by at least one year with the predefined window of interest: 2200 -- 800 calBC. (`r r("size dates_time_selection", sf_prep)` dates)

5. Reducing the date selection to all dates taken from graves as indicated by the *feature type* variable. (`r r("size dates_research_selection", sf_prep)` dates)

@@

8. Reducing date selection to dates within the research area. (`r r("size dates_research_area", sf_prep)` dates)

9. Removing ^14^C date doubles with tools of c14bazAAR. (`r r("size dates_prepared", sf_prep)` dates)

10. Transforming data from the meaning *^14^C dates on graves* to *burial type at a certain time*. For `r r("dates_research_area multi dates one grave", sf_prep)` entries in the thus far assembled subset the attribution to *site* and *feature* is not unique. That means that for many graves multiple (up to 8) ^14^C dates have been created (and entered in Radon-B) and dates therefore cannot be treated as semantically equal to graves. There is a variety of phenomena that cause this effect: In some cases, safety measurements were taken so that there are multiple dates for one single grave that all fall within the margin of errors of each other. In other cases, the set of dates for one grave strongly diverge because they cover the life cycle of a collective grave that was used for hundreds of years. There are also cases where the *feature* information in Radon-B is not sufficient to determine whether two dates are really from the same grave despite the identical entry. The following steps were applied to solve this problem algorithmically. The approach is compatible with the intention to create a cultural trait time series as explained below. (`r r("size graves_prepared", sf_prep)` graves)

@@

    2. For the remaining `r r("dates_prepared multi dates one grave with numbers", sf_prep)` problematic cases, groups were created by *site* and *feature*. The cumulated timespan covered by the $2\sigma$ age range of all these dates were taken as the relevant timespan for the respective grave.
